Slavnov products and KP tau functions

### 2025-04-25 draft.tex
start introduction

@@

One important ingredient in the Algebraic Bethe Ansatz is the scalar
product of Bethe states.  The is many important results on this topic,
see~\cite{Korepin:1993kvr} and references therein. Here we focus on
the scalar product between an on-shell and an off-shell Bethe vectors,
the so called \emph{Slavnov product}.

It is known that scalars products in the algebraic Bethe ansatz 
can be written as determinants. In~\cite{Belliard:2019bfz}, the
authors show the reason behind this fact. Let us start
with a short review of this work.

>>>>

One important ingredient in the Algebraic Bethe Ansatz is the scalar
product of Bethe states.  There are many important results on this
topic, see~\cite{Korepin:1993kvr} and references therein, but here we
turn our attention to the well known fact that scalars products in
the algebraic Bethe ansatz can be written as determinants.

More specifically, we will investigate a particular type of
correlation functions in quantum integrable spin chains, the so called
\emph{Slavnov product}~\cite{Slavnov1989}. These objects can be seen as building blocks
of more sofisticated correlation functions and are instrumental in the
study of norms of Bethe wave functions~\cite{Korepin:1993kvr}.  But
more importantly for our present discussion, Slavnov products seem to
be a bridge connecting quantum and classical integrable system.

The study of connections between classical and quantum integrable
systems is an old subject, and has been addressed from a wide range of
perspectives~\cite{Wu:1975mw, Its:1992bj, korepin2000the, Foda2009,
  Alexandrov:2011aa}.  In~\cite{Foda:2009zz}, the authors started the
analysis of the connections between the Slavnov products of the
Heisenberg XXZ spin chain, and the Kadomtsev–Petviashvili (KP)
classical integrable hierarchy. This analysis has been extended to
some directions and applications, for example~\cite{Wheeler:2010vmq,
  Foda:2010, Takasaki:2010qm, Foda:2012wn, Foda:2012wf}.

In (my papers)
the author of the current paper started studying some other cases of
this interesting connection, in particular, in the case of the Temperley-Lieb spin chains
and the Q-Boson model. In all these cases, although the specific details of he
Slavnov product are radically different, the general functional structure
are basically the same, modulo some multiplicative terms.

In~\cite{Belliard:2019bfz}, the authors show
the reason behind this fact.

@@

This section reviews the main arguments in~\cite{Belliard:2019bfz}.
